\documentclass[11pt,letterpaper]{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
% \usepackage{lastpage}%
%

% Based off of the below:
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------


\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{lmodern}

% set all the margins to .15cm
\usepackage[margin=0.9in]{geometry}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage[dvipsnames]{xcolor}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
% declare that the font can support any size

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{document}%
\normalsize%
\begin{center}
%
    \textbf{\Huge \scshape Nicholas Zolton} \\ \vspace{1pt}
%
    \small \href{tel:281{-}913{-}9227}{\underline{281{-}913{-}9227}} $|$ 
%
    \small \href{mailto:nicholaszolton@gmail.com}{\underline{nicholaszolton@gmail.com}} $|$ 
%
\small \href{https://nicholaszolton.dev/}{\underline{nicholaszolton.dev/}} $|$ 
%
\small \href{https://github.com/NicholasZolton}{\underline{github.com/NicholasZolton}}
%
\end{center}
%

%-----------PROGRAMMING SKILLS-----------
%
\section{Technical Skills}
%
 \begin{itemize}[leftmargin=0.15in, label={}]
%
    \small{\item{
%
     \textbf{Programming Languages}{: Java, C\#, C++, C, Python, JavaScript, TypeScript, HTML, CSS} \\
%
     \textbf{Tools/Frameworks}{: Git, React, React Native, NodeJS, Spring, Docker, Kubernetes, FastAPI, Flask, Svelte} \\
%
    }}
%
 \end{itemize}

\vspace{-18pt}
%
%-------------------------------------------
%
%-----------EXPERIENCE-----------
%
\section{Experience}
%
  \resumeSubHeadingListStart

    \resumeSubheading
%
      {Software Engineer}{February 2025 - Present}
%
      {Walmart Global Tech - Global Workforce Management Analytics Team}{Bentonville, AR}

      \resumeItemListStart
%
        \resumeItem{Eliminated \$1,000,000s in third-party contract costs by integrating Walmart Canada into our analytics platform.}

        \resumeItem{Designed and implemented data pipelines using Apache Airflow and BigQuery to build and deploy core analytics infrastructure, enabling business leadership to make data-driven decisions regarding labor demand and scheduling.}
%
        \resumeItem{Established robust monitoring, alerting, and data correction processes, focusing on key golden signals to ensure metric accuracy and significantly improve the reliability of business decision systems.}

        \resumeItem{Enhanced performance and delivered key features for a web application serving 60,000 daily active users by leveraging React, Node, and Redux, improving user satisfaction and system reliability.}
%
      \resumeItemListEnd

    \resumeSubheading
%
      {Software Engineering Intern}{June 2024 - August 2024}
%
      {Walmart Global Tech - Global Workforce Management Demand Team}{Bentonville, AR}
%
      \resumeItemListStart

        \resumeItem{Developed and deployed critical infrastructure components using Java Spring for the Global Workforce Management Demand team, directly supporting the scheduling system for 2.3 million associates worldwide.}
%
        \resumeItem{Built a microservice using Java Spring to meet business stakeholder needs, and saved 10s of hours each month of labor which required critical accuracy.}

        \resumeItem{Reduced tech debt by 30\% on all of our teams projects by refactoring and rewriting legacy code, which greatly increased the speed of further development and lowered overall maintenance costs significantly.}
%
      \resumeItemListEnd
  
%
    \resumeSubheading
%
      {Software Development Intern}{November 2022 – May 2023}
%
      {Truist Financial Corporation}{Richardson, TX}
%
      \resumeItemListStart

      \resumeItem{Optimized C\# and SQL stored procedures for W-2 services, reducing report generation time by up to 30 seconds.}
%
      \resumeItem{Maintained and upgraded core .NET infrastructure for user-facing services, ensuring high availability and low latency.}
%
      \resumeItemListEnd
%
    \resumeSubheading
%
      {Software Engineering Intern}{December 2021 – July 2022}
%
      {Brains4Drones}{Richardson, TX}
%
      \resumeItemListStart
%
        \resumeItem{Pioneered the adoption of Docker containerization within embedded systems, significantly enhancing code portability.}
%
        \resumeItem{Actively contributed to critical open source computer vision projects, including the YOLOv5 detection model.}
%
      \resumeItemListEnd
%
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
%
\section{Education}
%
\resumeSubHeadingListStart
%
\resumeSubheading
%
{University of Texas at Dallas}{GPA: 4.0}
%
{Bachelor of Science in Computer Science}{December 2024}

\resumeSubHeadingListEnd
%
%-----------PROJECTS-----------
%
\section{Projects}

  \resumeSubHeadingListStart
      \vspace{-5pt}
%
      \resumeProjectHeading
%
          {\textbf{Sparrow Link} $|$ \emph{FastAPI, Postgres, React, Typescript}}{April 2023}
%
          \resumeItemListStart
%
            \resumeItem{1st place Engineering Capstone project at The University of Texas at Dallas.}
%
            \resumeItem{Developed a remote research platform for Spark Biomedical, accelerating clinical trials and data collection for their tAN device by enabling secure remote access to medical technology.}
%
          \resumeItemListEnd

      \vspace{-5pt}
%
      \resumeProjectHeading
%
          {\textbf{Redwood} $|$ \emph{Python, React, JavaScript, FastAPI}}{November 2023}
%
          \resumeItemListStart
%
            \resumeItem{Finalist project at HackPrinceton 2023.}
%
            \resumeItem{Leveraged topological sort to generate a learning path which determines the shortest path of knowledge for users to learn a complex topic using SpaCy.}
%
          \resumeItemListEnd
%
    \resumeSubHeadingListEnd

%
%-----------ACHIEVEMENTS SECTION-----------
%
\section{Achievements}
%
 \begin{itemize}[leftmargin=0.15in, label={}]
%
    \small{\item{
    
    \textbf{Google Developer Student Club President} \hfill {2023 {-} 2024} \\
%
     \textbf{HackPrinceton 2023 Finalist} \hfill {November 2023} \\

     \textbf{HackRICE 13 Hackathon 2nd Place Environmental Hack} \hfill {September 2023} \\
%
     \textbf{Axxess 2023 Hackathon Overall 1st Place} \hfill {April 2023} \\
%
     \textbf{HackUTA 2023 Overall 2nd Place} \hfill {October 2023} \\
%
     \textbf{WEHack 2023 Hackathon 2nd Place Machine Learning} \hfill {February 2023} \\
%

     \textbf{1st Place Engineering Capstone Project at UTD} \hfill {December 2024} \\
%
    }}
%
 \end{itemize}
%

%
\end{document}
